Exploring Disparate Data: Part 1

### 2024-11-04 A3-Pt1.Rmd

-   Aditya (169027493)
-   Andy
-   Dibu (169708451)
-   Oscar
-   Taras

@@

```{r error=TRUE}
# YOUR CODE HERE
cyclones_data_update_0 <- bind_rows(at_cyclone, np_cyclone)
print(cyclones_data_update_0)
```

@@

```{r cyclones_data_update_2, error=TRUE}
cyclones_data_update_2 <- cyclones_data_update_1 |>
    mutate(
        date = make_datetime(ObservYear, Month, Day, Hour * 100 + Minute)
    )

@@

cyclones_data <- cyclones_data_update_2 |>
    mutate(
        category = ordered(
            case_when(
                # YOUR CODE HERE
                max_wind < 34 ~ "TD",
                max_wind >= 34 & max_wind < 64 ~ "TS",
                max_wind >= 64 & max_wind < 83 ~ "1",
                max_wind >= 83 & max_wind < 96 ~ "2",
                max_wind >= 96 & max_wind < 113 ~ "3",
                max_wind >= 113 & max_wind < 137 ~ "4",
                max_wind >= 137 ~ "5"

@@

```{r}
# YOUR CODE HERE
write_parquet(cyclones_data, "cyclones_data.parquet")
```

@@

```{r}
ice_extent_yearly <- ice_extent_daily |>
    # YOUR CODE HERE
    group_by(year, region) |>
    summarize(
        min = min(ice_extent, na.rm = TRUE),
        max = max(ice_extent, na.rm = TRUE),
        .groups = "drop"
    ) |>
    pivot_longer(
        cols = c("min", "max"),
        names_to = "name",
        values_to = "value"
    )
ice_extent_yearly
```

@@

```{r sea_ice_parquet, error=TRUE}
# YOUR CODE HERE
write_parquet(ice_extent_yearly, "ice_extent_yearly.parquet")
```

@@

```{r happiness}
happiness <- read.xlsx("DataForTable2.1.xlsx") |>
  clean_names() |>
  rename(
    "country" = country_name
  ) |>
  filter(
    !is.na(life_ladder)
  ) |>
  group_by(
    country
  ) |>
  slice_max(
    order_by = year
  )

>>>>

-   Andy (169081356)
-   Dibu (169708451)
-   Oscar (169057882)
-   Taras (169099616)

@@

```{r error=TRUE}
cyclones_data_update_0 <- bind_rows(at_cyclone, np_cyclone)
print(cyclones_data_update_0)
```

@@

```{r cyclones_data_update_2, error=TRUE}
cyclones_data_update_2 <- cyclones_data_update_1 |>
    mutate(
        date = make_datetime(year = ObservYear,month = Month, day = Day, hour = Hour, min = Minute)
    )

@@

cyclones_data <- cyclones_data_update_2 |>
    mutate(
        category = ordered(
            case_when(
                max_wind < 34 ~ "TD",
                max_wind >= 34 & max_wind < 64 ~ "TS",
                max_wind >= 64 & max_wind < 83 ~ "1",
                max_wind >= 83 & max_wind < 96 ~ "2",
                max_wind >= 96 & max_wind < 113 ~ "3",
                max_wind >= 113 & max_wind < 137 ~ "4",
                max_wind >= 137 ~ "5"

@@

```{r}
write_parquet(cyclones_data, "cyclones_data.parquet")
```

@@

```{r}
ice_extent_yearly <- ice_extent_daily |>
    group_by(year, region) |>
    summarize(
        min = min(ice_extent, na.rm = TRUE),
        max = max(ice_extent, na.rm = TRUE),
        .groups = "drop"
    ) |>
    pivot_longer(
        cols = c("min", "max"),
        names_to = "name",
        values_to = "value"
    )
ice_extent_yearly
```

@@

```{r sea_ice_parquet, error=TRUE}
write_parquet(ice_extent_yearly, "ice_extent_yearly.parquet")
```

@@

```{r happiness}
happiness <- read.xlsx("DataForTable2.1.xlsx") |>
  janitor :: clean_names() |> 
  rename(
    country = country_name
  ) |>
  filter(!(is.na(life_ladder)))|>
group_by(country) |>                 
  arrange(country, desc(year)) |>      
  slice(1)
